---
#title: "Paired Pulse Ratio Extraction"
author: "Haley E. Speed, PhD"
output: html_notebook
---

<h3>"Paired Pulse Ratio Extraction"</h3>
Turns Clampfit average trace results into clean paired pulse ratios.

<h4>Assumptions </h4>
- Traces were averaged for each interstimulus interval
- Slopes of each interstimulus interval were measured for each sweep 

<h4>Variables that may need to be changed:</h4>
- <b>intervals</b> <- number of interstimulus intervals
- <b>order</b> <- order of interval presentation

<h4>The default for the Powell Lab Paired Pulse Cycles protocol (Speed et al., 2012, 2013, 2015) are:</h4>
- <b> intervals </b> <- 6
- <b> order </b> <- c(50 ms, 500 ms, 100 ms, 80 ms, 30 ms, 200 ms)


```{r}
# Variables to be changed by user
intervals <- 6 # Number of interstimulus intervals

# Order of interval presentation (rows of spreadsheet)
order <- c(50,500,100,80,30,200)

```

```{r}

# Do not change this section unless you really know what you are doing
library(knitr)
library(openxlsx)

getDir <- function (){
        file.inDir <- readline("Enter the path to the working directory: ")
        return (file.inDir)
}
getFile <- function(){
        file.inSlope <- readline("Enter the filename of slope data: ")
        return (file.inSlope)
}

getDataTables <- function (file.name, file.dir) {
        setwd(file.dir)
        file.data <- read.xlsx(file.name, sheet =  1, colNames=TRUE)
        return(file.data)
}

```

```{r}

# Get working directory from the user
file.dir <- getDir() # if you get "Error: Unexpected Error...." click here and choose "run selected lines" from the "Run" button

```

```{r}
# Get filename from user (may have to add ".xlsx" if you have file extensions hidden in the file explorer)
file.name <- getFile() # if you get "Error: Unexpected Error...." click here and choose "run selected lines" from the "Run" button

```

```{r}
# Read in data from each file 
slope.data  <- getDataTables(file.name, file.dir)
print (slope.data)
```

```{r}
# Calculations - Do Not Change
# Warning "NAs introduced by coersion" may be ignored
output <- data.frame(interval = character(), slope1 = numeric(), slope2 = numeric(), ppr = numeric())
row <- 1
while (row <= length(slope.data$slope1)){
  sorted <- sort(as.numeric(slope.data[row,]))
  sorted1 <- sorted[1]
  sorted2 <- sorted[2]

  if (slope.data$slope1[row] == sorted1) { 
    slope1 <- sorted1
    slope2 <- sorted2
  } else if (slope.data$slope1[row] == sorted2) { 
    slope1 <- sorted2
    slope2 <- sorted1
  }
  ppr <- slope2 / slope1
  rowData <- cbind( interval = order[row], slope1 = slope1, slope2 = slope2, ppr = ppr)
  output <- rbind(output, rowData)
  row <- row + 1
}

output <- output[order(-output$ppr),]
output <- cbind(Trace = row.names(output), output) 

print(output)


```

```{r}
file.outDir <- paste(file.dir,"extracted", sep = "\\")
if (!dir.exists(file.outDir)) { dir.create(file.outDir) }
file.baseName <- strsplit( file.name, ".xlsx")
print(file.baseName)
file.outName <- paste(file.baseName, "analyzed", sep = "_")
file.outName <- paste(file.outName, "csv", sep = ".")
file.out <- paste(file.outDir, file.outName, sep = "\\")
write.csv(output, file.out, row.names = FALSE)
```


